Cognate beginnings to bilingual lexical acquisition

### 2023-07-06 manuscript/_appendix/_model-doe.qmd
Fix appendix

As a robustness check, we fit a model similar to the one described in the main manuscript, but including lexical frequency and language degree of exposure as separate predictors, instead of the composite measure *Exposure*. Language degree of exposure (*DoE*) was included in interaction with *Age* and *Cognateness*, while lexical frequency (*Frequency*) was included as a main effect.

```{r fig-coefs-doe}
#| label: fig-coefs-doe
#| fig-cap: "Posterior distribution of regression coefficients of the model including the *Exposure* composite predictor, and of the model including lexical frequency and degree of exposure (DoE) separately. Dots and error bars indicate the median and 95% HDI of the posterior distribution of each coefficient. Coefficients of the *Exposure* model are indicated in grey with triangles. Coefficients of the *Frequency + DoE* model are indicated in black with circless. The region of practical equivalence (ROPE) around zero is indicated with a grey area and a grey line."
#| fig-note: ""
#| echo: false
#| message: false
#| warning: false
#| out-width: 100%
#| fig-height: 4
#| fig-width: 7
# summarise posterior draws
bind_rows("Exposure model" = model_summary,
          "DoE-Frequency model" = posterior_doe_summary,
          .id = "model") |> 
    mutate(
        across(c(.median, .lower, .upper),
               function(x) {
                   ifelse(
                       .type=="Intercepts (at 22 months)",
                       plogis(x),
                       x/4
                   )
               }
        )) |>
    filter(.type == "Slopes") |> 
    ggplot(aes(.median, .variable_name,
               xmin = .lower, xmax = .upper,
               colour = model,
               shape = model)) +
    annotate(geom = "rect",
             ymin = -Inf,
             ymax = Inf,
             xmin = -0.1/4,
             xmax = +0.1/4,
             fill = "grey90") +
    geom_vline(xintercept = 0, 
               linetype = "dashed",
               linewidth = 3/4,
               colour = "grey") +
    geom_errorbar(linewidth = 3/4, 
                  position = position_dodge(width = 0.5),
                  width = 0.3) +
    geom_point(size = 2.5,
               position = position_dodge(width = 0.5)) +
    labs(x = "Median and 95% HDI of the posterior distribution",
         y = "Predictor",
         colour = "Model") +
    scale_colour_grey(start = 0, end = 0.6) +
    theme(legend.position = "none",
          axis.title.y = element_blank(),
          panel.grid.major.y = element_blank())
```

>>>>

As a robustness check, we fit a model similar to the one described in the main manuscript, but including lexical frequency and language degree of exposure as separate predictors, instead of the composite measure *Exposure*. Language degree of exposure (*DoE*) was included in interaction with *Age* and *Cognateness*, while lexical frequency (*Frequency*) was included as a main effect. @tbl-coefs-doe shows a comparison between the posterior distribution of the regression coefficients of both models. Overall, results are equivalent.

```{r tbl-coefs-doe}
#| label: tbl-coefs-doe
#| fig-cap: "Posterior distribution of regression coefficients of the model including the *Exposure* composite predictor, and of the model including lexical frequency (*Frequency*) and degree of exposure (*DoE*) separately. Median: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution. p(ROPE): overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero. In the right column, we show a graphical representation of the median and 95% HDI of each coefficient, with a reference dotted line indicating the location of zero."
#| echo: false
#| message: false
#| warning: false
# summarise posterior draws
tbl_data <- bind_rows("Exposure model" = model_summary,
                      "DoE-Frequency model" = posterior_doe_summary,
                      .id = ".model") |> 
    mutate(
        across(c(.median, .lower, .upper),
               function(x) {
                   ifelse(
                       .type=="Intercepts (at 22 months)",
                       plogis(x),
                       x/4
                   )
               }
        )) |>
    filter(.type == "Slopes") |> 
    select(.model, .variable_name, .median, .lower, .upper, .rope_overlap) |> 
    mutate(
        across(.median:.upper, plogis),
        .variable_name = gsub("×", '$\\\\times$', .variable_name),
        .hdi = paste0("[", round(.lower, 3),
                      ", ", round(.upper, 3), "]"),
        .rope_overlap = sub("^(-?)0.", "\\1.",
                            sprintf("%.3f", .rope_overlap))) |> 
    select(.variable_name, .median, .lower, .upper, .hdi, .rope_overlap)

tbl_data |> 
    mutate(viz = "") |> 
    select(-c(.lower, .upper)) |> 
    knitr::kable(
        format = "latex", 
        escape = FALSE,
        col.names = c("",
                      "$\\beta$",
                      "95\\% HDI",
                      "$p(\\text{ROPE})$",
                      ""),
        digits = 3,
        booktabs = TRUE,
        align = "lclr",
        linesep = ""
    ) |> 
    kableExtra::pack_rows("Model: Exposure",
                          start_row = 1,
                          end_row = 8) |> 
    kableExtra::pack_rows("Model: Frequency & DoE",
                          start_row = 9,
                          end_row = 17)
```
